Unified data structures for solving optimally a set of interrelated computational geometry problems

### 2020-01-08 eurocg20/article-eurocg20.tex
euroCG 2020 & extended abstract

%TODO mandatory: add short abstract of the document
\begin{abstract}
	The paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems. To do this, a unified algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources. We build the environment on the basis of the ``divide and conquer'' strategy. 
	Once a convex hull is key to a set of computational geometry problems, we offer a concatenable queue data structure to maintain it. The data structure is implemented in a form of a binary tree. This allows to perform operations needed in algorithm for a set of problems in $O(\log n)$ time. Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
	In the future the algorithmic environment can be improved to support other computational models with similar properties for solving problems. As an example, the Voronoi diagram or the Delaunay triangulation can be considered.
\end{abstract}

@@

	Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of problems. The core of this set are problems of computational geometry and computer graphics. To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time. Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy. It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems such as in \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}. Every such algorithm requires its own computational resources and is executed independently from others. In such case some identical steps, such as preprocessing and building data structures, are performed several times.

@@

\bibliography{article-SoCG}
\end{document}

>>>>

\begin{abstract}
	This paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems. To do this, a unified algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources. We build the environment on the basis of the ``divide and conquer'' strategy. 
 	Once a convex hull is key to a set of computational geometry problems, we offer a concatenable queue data structure to maintain it. The data structure is implemented in a form of a binary tree. This allows to perform operations needed in algorithm for a set of problems in $O(\log n)$ time. Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
	In the future the algorithmic environment can be improved to support other computational models with similar properties for solving problems. As an example, the Voronoi diagram or the Delaunay triangulation can be considered.
\end{abstract}

@@

	Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of problems. The core of this set are problems of computational geometry and computer graphics. To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time. Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package do not result in desirable efficiency and accuracy. It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems such as in \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}. Every such algorithm requires its own computational resources and is executed independently from others. In such case some identical steps, such as preprocessing and building data structures, are performed several times.

@@

\bibliography{article-eurocg20}
\end{document}
